### 2015-10-13 weeklyReport/motivating.tex
10-13-15,problem to return structured code examples

%\section{Motivating Example}

>>>>

\input{example-scenario}
%\section{Motivating Example}
\section{Usage Scenario}
\noindent{\textbf{Add undo and redo action for TextEditor.}}

\begin{table}[ht]
\begin{center}
\caption{Search Result from Code Search Engine}
\label{tab:total}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}c|llrr@{}} \hline
No.&Name&Project&LOC&\# M\\\hline
1&TextEditor&textmash&1270&12\\
2,3&AndroidTextEditor&android&576&9\\
4&DocumentUndoManagerImpl&ide&1227&17\\
5,6,8&ConsoleTextEditor&groovy&321&7\\ 
7&PapyrusCDTEditor&eclipse.papyrus&393&7\\
9,10&AspectEditorContributor&eclipse&88&2\\ \hline
\end{tabular*}
 \label{tab:undoResult}
 \textbf{ \# M} represents the number of methods that contain the query terms. 
 {\bf No.} represents the rank from CSE. Note that CSE may return the same results for multiple times, as the same file may exist in multiple branches. For instance, we regard 5,6,8 as identical with manual inspection.

}
 \end{center}
\end{table}

To further illustrate that reuse task involves in multiple methods and classes, and the reuse task is hard without tool support, I imagine a scenario that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons, inspired by the evaluation task used in~\cite{Murphy:nlConcern11}. Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}. Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11} and blue part represents source code that implements this feature.  Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE. We find that all code examples require multiple methods and classes to implement a feature. We also find that all code examples include other auxiliary features that are not directed related to the undo and redo feature.

We assume that user provides a seed code example for the reuse task. She selects the first result from CSE. She uses keyword search to locate undo and redo feature in 6 methods and regards them as  seed API calls. Shown in Figure~\ref{fig:undoEditor}, she removes  the other  11 methods (865 LOC) that she regards as irrelevant to her reuse task. She recognizes that she needs to implement an \codefont{UndoAction} and \codefont{RedoAction} which are the subclass of \codefont{AbstractAction}, and overrides their actionPerform() method. In the actionPerformed() methods, she should invokes the \codefont{CompoundUndoManager.undo()} and  \codefont{CompoundUndoManager.redo()} correspondingly. Without knowing anything about \codefont{CompoundUndoManager}, she has to query CSE again for `CompoundUndoManager textmash'. This class consists of 17 methods (221 LOC) and she has to repeat to keyword search again to locate undo and redo feature in this class. With manual inspection, she notices that this \codefont{CompoundUndoManager} is a subclass of \codefont{javax.swing.UndoManager} and it overrides four methods \{\codefont{canUndo, canRedo, undo, redo}\} that are related to the feature. She notices that she actually does not need this \codefont{CompoundUndoManager} and decides to invoke its parent class \codefont{UndoManager}  instead. She also notices that she does not need the \codefont{CannotRedoException} by using \codefont{UndoManager}.

After she integrates \codefont{UndoManager, UndoAction, and RedoAction} to her context, she tests it and it fails to perform the feature. She has to look at other examples, and she finds the No.5 example returned from CSE.  This example seems promising because it is also an implementation of a TextEditor. She notice that  the API \codefont{doc.addUndoableEditListener (undoManager)} seems the one that she misses now, but again, she has to investigate the class   \codefont{TextUndoManager} again.

With this example, we illustrate that salient API calls that implement a desired feature are always interleaving with other related elements. To finish a reuse task, developer has to remove irrelevant parts.  However, it  requires significant effort to tease out these auxiliary features without tool support. Since the examples always contain both main feature and auxiliary features,  there seldom exists a perfect example for reuse and developers has to iteratively search for new examples and integrate it to their context until the integration results are examined.

\section{Problem 3}
Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.

Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.

%We use the results for  the last three concerns implementation in Table~\ref{tab:concern} found by the code search engine SearchCode to illustrate the Problem 3.

%  a feature location approach that is similar to~\cite{Denys:FCA12} to identify seed API calls shown in Figure~\ref{fig:undoEditor}. We remove the other  11 methods (865 LOC) that we believe is irrelevant to our reuse task.

%For each partial program returned from CSE, we select the top k (k=5) methods that are related to the given query. I present No. 1, 5, 6, 8 to show that it requires multiple methods and classes to implement a concern. The other four examples are shown in Appendix.

%In this example, we use feature location approach~\cite{Denys:FCA12} to identify salient API calls,

### 2015-10-13 weeklyReport/problem.tex
10-13-15,problem to return structured code examples

\section{Problem Statement}

Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.  In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.  During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.

>>>>

\section{Last week}

Based on our discussion last week, our problem statement includes:

\begin{enumerate}
\item Developers do not know the name of API elements a priori, though locating code example through existing search engine often expects the developers to know API elements' names.
\item Reuse tasks involve multiple related classes and methods, rather than a single method/class. Yet code search engines do not help developers recognize the latent structure among related classes/methods. (at the granularity of multiple methods)
\item During copy/paste based reuse, developers must remove irrelevant parts. Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts. (at the granularity of multiple examples)
\end{enumerate}

We have three hypotheses correspondingly:
\begin{enumerate}
\item We believe that NLP text with partial code snippet could help us identify the name of API elements based on keywords from free-form query.

\item Our hypothesis is that we can find related elements by following the structural dependencies of seed API elements in code and by ranking other API elements potentially mentioned in natural language text.

\item We believe that clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.

\end{enumerate}

I focus on the second  problem, and perform a preliminary study using popular code search engines to illustrate this problem.

\input{example}
\input{eval-table}
\section{Problem 2}
Problem: Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.

Hypothesis: We can find and rank related elements by following the structural dependencies of seed API elements in code.

Input: a free-form query that user provides to present her reuse intention.

Output: a list of classes/methods implementation that complete this reuse task.

Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?

To answer these two subquestions, I search for the evaluation dataset for existing feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04} shown in Table~\ref{tab:concern},    reuse tools~\cite{Holmes:reuse07, Holmes:ASE09} shown in Table~\ref{tab:reuse}, and code search tools using free-form query ~\cite{sniff:Sen09, Portfolio:DenysICSE11, Sourcerer:SC14, Gvero:ICSE15, spotWork:ICSE14} shown in Table~\ref{tab:freeform}. We find that most medium-scale or large-scale reuse tasks involve multiple methods and classes,  and the developer should implement multiple methods and classes to finish the reuse task. Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code snippet already exist. We argue that this assumption might not hold for a non-trivial reuse task, because developers need to implement the salient API calls that provide the main functionality as well as other related elements based on the latent structure.

% existing code search tools and  feature location tools  do not help developers recognize the latent structure among related classes/methods.

%Other code search engines such as Koders~\cite{Koders}, Krugle~\cite{Krugle}, and SearchCode~\cite{SearchCode} are available on the web, %which can be used to assist programmers by providing relevant code examples with usages of the given free-form query from a large number of public source code repositories. 
%yet the results are sorted based on the text matching and they also fail to recognize the latent structure among related classes/methods.

%Based on Table~\ref{tab:concern} and Table~\ref{tab:reuse}, most medium-scale or large-scale reuse tasks involve multiple methods and classes.  However, existing code search tools and  feature location tools  do not help developers recognize the latent structure among related classes/methods. We do not focus on large-scale reuse task mentioned in~\cite{Holmes:reuse07, Holmes:ASE09}.

%In summary,  a feature/concern reuse task involves multiple related classes and methods. The developer should implement multiple methods and classes to finish the reuse task. Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code already exist. We argue that it requires multiple methods to implement a non-trivial feature/concern.

%\subsection{Problem 3}
%Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.

%Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.

%We use the results for  the last three concerns implementation in Table~\ref{tab:concern} found by the code search engine SearchCode to illustrate the Problem 3.

\begin{comment}
Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.  In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.  During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.

### 2015-10-13 weeklyReport/related.tex
10-13-15,problem to return structured code examples

\section{Related Work}
\input{table}
\noindent{\textbf{Extract partial program from informal documentation.}}  Lightweight regular expressions and information retrieval techniques have been widely used to resolve the links between source code elements and documentations. Bacchelli et al.~\cite{Bacchelli:emailICSE10} use regular expressions to  identify code elements in email discussions based on programming naming conventions. Antoniol et al.~\cite{Antoniol:Link02} apply a probabilistic Vector Space Model to resolve terms while Marcus et al.~\cite{Marcus:LinkICSE03} use Latent Semantic Indexing to recover links. However, both regular expression and information retrieval techniques suffer from a low precision and recall around 0.5. RecoDoc~\cite{RecoDoc:ICSE12} leverages term context to extract code-like terms and use partial program analysis~\cite{partialProgram:OOPSLA08} and a set of structural/lexical heuristic filters to resolve ambiguous terms. ACE~\cite{PeterACE:ICSE13} extends RecoDoc with island parser to identify code-like terms and reparses each document to resolve ambiguous terms using term's context. We leverage ACE to extract partial program from informal documentations and use partial program analysis~\cite{partialProgram:OOPSLA08}  to infer type declaration and resolve method binding ambiguity. We advance these tools in the sense that we not only identify partial program as code example, but also help cluster similar examples and integrate reusable examples to the target context.

\noindent{\textbf{Cluster code examples.}} 
Our example clustering approach is similar to some prior works that extract representative examples for specific APIs or user query. MAPO~\cite{MAPO:ECOOP09} leverages frequent call sequences to cluster the usage of specific APIs and rank abstract usage patterns based on the context similarity. Buse et al\/\cite{Buse:apiICSE12} propose to generate abstract API usages by synthesizing code examples using symbolic execution for a particular API. Different from these works that generate abstract usage patterns for specific API or data type, SNIFF~\cite{sniff:Sen09} performs type-based intersection of code chunks based on the keywords in the free-form query and cluster the common part of the code chunks for concrete code examples. However, these works   only focus on providing code examples based on the popularity or textural relevance while developers have to manually resolve structural dependencies before reusing the examples.   MUSE~\cite{MUSE:MarcusICSE15} addresses this limitation using slicing to generate concrete usage examples and selects the most representative ones based on the popularity and readability while  Keivanloo et al\/\cite{spotWork:ICSE14} uses clone detection to cluster examples involving loops and conditions. We make it one step further to support partial code example clustering and identify structural correspondence to identify both common features and alternative features. PRIME~\cite{Prime:OOPSLA12} supports code search over partial programs based on type state transition, yet it requires users to provide partial temporal specification for generalized {\it typestate}.  There exists a number of code example suggestion tools that recommend call chains~\cite{Mandelin:jungloid05, parseWeb:ASE07, Xsnippet:OOPSLA06} or related functions~\cite{Export:DenysASE13, Portfolio:DenysICSE11} based on queries~\cite{Sourcerer:SC14} or contexts~\cite{Holmes:structural05, Prompter:MSR14}. But these tools can only recommend code examples in the method level which make them insufficient for  reuse tasks across multiple classes.

>>>>

\section{Related Work}
%\input{table}
%\noindent{\textbf{Extract partial program from informal documentation.}}  Lightweight regular expressions and information retrieval techniques have been widely used to resolve the links between source code elements and documentations. Bacchelli et al.~\cite{Bacchelli:emailICSE10} use regular expressions to  identify code elements in email discussions based on programming naming conventions. Antoniol et al.~\cite{Antoniol:Link02} apply a probabilistic Vector Space Model to resolve terms while Marcus et al.~\cite{Marcus:LinkICSE03} use Latent Semantic Indexing to recover links. However, both regular expression and information retrieval techniques suffer from a low precision and recall around 0.5. RecoDoc~\cite{RecoDoc:ICSE12} leverages term context to extract code-like terms and use partial program analysis~\cite{partialProgram:OOPSLA08} and a set of structural/lexical heuristic filters to resolve ambiguous terms. ACE~\cite{PeterACE:ICSE13} extends RecoDoc with island parser to identify code-like terms and reparses each document to resolve ambiguous terms using term's context. We leverage ACE to extract partial program from informal documentations and use partial program analysis~\cite{partialProgram:OOPSLA08}  to infer type declaration and resolve method binding ambiguity. We advance these tools in the sense that we not only identify partial program as code example, but also help cluster similar examples and integrate reusable examples to the target context. 
\noindent{\textbf{Feature Location Tools.}}  Poshyvanyk et al.~\cite{Denys:FCA12} use information retrieval approach to locate a queried feature in source code. They  evaluate the similarity between documents and user query and cluster the source code based on formal concept analysis.  Portforlio~\cite{Portfolio:DenysICSE11} and Export~\cite{Export:DenysASE13} identify related functions by combining both latent structure similarity and lexical information similarity. Our feature location approach is similar to~\cite{Portfolio:DenysICSE11} yet we focus on suggesting implementation for the feature rather than identify feature location.
Rastkar et al.~\cite{Murphy:nlConcern11} summarize the structure of multiple instances of a crosscutting concern in natural language, yet they only extract structural facts in the level of method signature and class hierarchy. We make it one step further to suggest feature implementation based on the context and user query.

%Hill et al.~\cite{Hill:FindConcept07} leverage natural language analysis to

\noindent{\textbf{Code Search Tools.}} 
Our example clustering approach is similar to some prior works that extract representative examples for specific APIs or user query. 
MAPO~\cite{MAPO:ECOOP09} leverages frequent call sequences to cluster the usage of specific APIs and rank abstract usage patterns based on the context similarity. Buse et al\/\cite{Buse:apiICSE12} propose to generate abstract API usages by synthesizing code examples using symbolic execution for a particular API. Different from these works that generate abstract usage patterns for specific API or data type, SNIFF~\cite{sniff:Sen09} performs type-based intersection of code chunks based on the keywords in the free-form query and cluster the common part of the code chunks for concrete code examples. However, these works   only focus on providing code examples based on the popularity or textural relevance while developers have to manually resolve structural dependencies before reusing the examples.  MUSE~\cite{MUSE:MarcusICSE15} addresses this limitation using slicing to generate concrete usage examples and selects the most representative ones based on the popularity and readability while  Keivanloo et al\/\cite{spotWork:ICSE14} uses clone detection to cluster examples involving loops and conditions. We make it one step further to  identify structural correspondence to identify both common features and alternative features.  There exists a number of code example suggestion tools that recommend call chains~\cite{Mandelin:jungloid05, parseWeb:ASE07, Xsnippet:OOPSLA06}  or contexts~\cite{Holmes:structural05, Prompter:MSR14}. But these tools can only recommend code examples in the method level which make them insufficient for  reuse tasks across multiple classes.
